Tracking $p$-adic precision

### 2014-02-24 padicprec.tex
Fix bibiography
Xavier's suggested changes

\section{Tracking Precision} \label{sec:prec-proposal}

@@

We recall some standard definitions from ultrametric analysis, referring to
Schneider \cite{schneider:11a} for a complete exposition.

@@

This definition encapsulates the main practical suggestion of the paper with regards to representing
vector spaces, matrices, polynomials and power series over $K$: one should \textbf{separate} the
approximation from the precision.  In the rest of this section we discuss some of the benefits made
possible by such a separation.

@@

\bibliographystyle{plain}
%\bibliography{roebib/Biblio}
\bibliography{Biblio}

>>>>

\section{Problems in Precision} \label{sec:prec-proposal}

We begin by offering two examples that illustrate key features of $p$-adic precision.
Recall that an element $a + O(p^N)$ of $\Qp$ has \emph{absolute precision} $N$ if
it is well defined up to adding an unknown element of $p^N\Zp$.

@@

In order to make our proposals for tracking precision clear, we need
some definitions from ultrametric analysis.  See 
Schneider \cite{schneider:11a} for a more complete exposition.

@@

The definition of an approximate element encapsulates the two main practical suggestions of this paper
with regards to representing vector spaces, matrices, polynomials and power series over $K$:
\begin{enumerate}
\item one should \textbf{separate} the approximation from the precision,
\item the appropriate object to represent precision is a \textbf{lattice}.
\end{enumerate}
In the rest of this section we discuss some of the benefits made possible these choices.

@@

\bibliographystyle{plain}
\bibliography{roebib/Biblio,extras}
